$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}=1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$

### 2020-02-21 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/prl.tex
updated

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 03 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by March 02, 2020}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$}
\input author_list.tex       % D0 authors (remove the first 3 lines
                             % of this file prior to submission, they
                             % contain a time stamp for the authorlist)
                             % (includes institutions and visitors)
\date{\today}

>>>>

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 04 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by March 02, 2020}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

%\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$}
\title{$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}=1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$}
\input authorlist.tex

\date{\today}
